Growth model analysis

### 2017-12-11 manuscriptAnalysis/MS_Analysis.Rmd
added removeUnsampledRows()
fixed summing over nAllFishBySpeciesP

```{r}
library(tidyverse)
d <- dddG[[1]]
#load(file = './data/out/ddD.RData')
load(file = './data/out/countsAndMasses.RData')
```

@@

  p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
    rename(est=est,species=d1,season=d2,river=d3,year=d4)
  ggplot(p, aes(year,invlogit(est))) +geom_point() + facet_grid(season ~ river + species)

@@

  tmp <- dddD[[2]] %>%
           group_by(riverOrdered,year,season,section) %>%
           summarize( s = sum(enc) ) %>%
           filter( s == 0 )
  table(tmp$riverOrdered,tmp$year,tmp$season)

@@

ggplot(d, aes(year,countPAllSpp)) +
  geom_point() +
  geom_line() +
  labs( x = "Year", y = "Estimated count") +
#  ylim(0,2500) +
  theme_publication() +
  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")

@@

ggplot(d, aes(year,countP.y,color=species)) +
  geom_point() +
  geom_line() +
  labs( x = "Year", y = "Estimated count") +
#  ylim(0,2500) +
  theme_publication() +
  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")
```

>>>>

```{r}
library(tidyverse)
d <- dddG[[1]]
load("D:/projects/linkedModels/data/out/ddD_bktbntats_1997.RData")
load("D:/projects/linkedModels/data/out/countsAndMasses.RData")
```

@@

  p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
    rename(est=est,species=d1,season=d2,river=d3,year=d4)
  ggplot(p, aes(year,invlogit(est))) +geom_point() + facet_grid(season ~ river + species)
  ggsave('figures/p.png')

@@

  # tmp <- dddD[[2]] %>%
  #          group_by(riverOrdered,year,season,section) %>%
  #          summarize( s = sum(enc) ) %>%
  #          filter( s == 0 )
  # table(tmp$riverOrdered,tmp$year,tmp$season)

@@

ggplot(d, aes(year,nAllFishP)) +
  geom_point() +
  geom_line() +
  labs( x = "Year", y = "Estimated count") +
#  ylim(0,2500) +
  theme_publication() +
  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")

@@

ggplot(d, aes(year,nAllFishBySpeciesP)) +
  geom_point(aes(color=species)) +
  geom_line(aes(color=species)) +
   geom_line(  aes(year,nAllFishP) ) +
  labs( x = "Year", y = "Estimated count") +
#  ylim(0,2500) +
  theme_publication() +
  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")
```
